---
title: "A1-Rachel-Jackson"
author: "Rachel Jackson"
date: "9/3/2020"
output:
  pdf_document: default
  html_document: default
---

# Prompt

Make four ggplot graphs using this "OJ" data set.

1. Use at least five different ggplot "geoms", one of which must be "geom_histogram".

2. Use "fill", "size", and "shape" ggplot "aesthetics".

3. Make sure each graph has a title and descriptive axes labels.

# Get our data

### Download

Import "OJ" data from R package.

```{r}
# install.packages("ISLR")
```

### Use the package

Load "OJ" data into running R environment and look at first 6 lines of data to understand the data better.

```{r}
library(ISLR)
head(OJ)
```

# Graph 1 - Bar Graph

(Used "fill" aesthetic in this graph)

```{r}
library("ggplot2")

g1 <- ggplot(data = OJ) +
  geom_bar(mapping = aes(x = StoreID, fill = Purchase), position = "dodge")

g1 + ggtitle("Plot of No. of Purchases \n by Store ID and Purchase Choice") +
  theme(plot.title = element_text(hjust = 0.5)) +
  xlab("Store ID Where Sale Occured") + ylab("No. of Purchases")

```

# Graph 2 -  Boxplot

```{r}
g2 <- ggplot(OJ, aes(x = Purchase, y = PriceCH)) +
  geom_boxplot()

g2 + ggtitle("Plot of Citrus Hill (CH) Price by Purchase Choice") +
  theme(plot.title = element_text(hjust = 0.5)) +
  xlab("Purchase of Citrus Hill (CH) or Minute Maid (MM)") + ylab("CH Price ($)")
```

# Graph 3 - Histogram

(Used "fill" aesthetic in this graph)

```{r}
g3 <- ggplot(OJ, aes(x=WeekofPurchase, color=Purchase)) +
  geom_histogram(fill="white", position="dodge") +
  theme(legend.position="top")

g3 + ggtitle("Plot of No. of Purchases \n by Week and Purchase Choice") +
  theme(plot.title = element_text(hjust = 0.5)) +
  xlab("Week of Purchase") + ylab("No. of Purchases")
```

# Graph 4 - Point Plot

(Used "size" aesthetic in this graph)

```{r}
g4 <- ggplot(data = OJ, mapping = aes(x = PriceCH, y = PriceMM)) +
  geom_point(mapping = aes(size = StoreID)) +
  geom_smooth()

g4 + ggtitle("Plot of Citrus Hill Price vs Minute Maid Price \n by Store ID") +
  theme(plot.title = element_text(hjust = 0.5)) +
  xlab("CH Price ($)") + ylab("MM Price ($)")
```

# Graph 5 - Point Plot

(Used "shape" aesthetic in this graph)

```{r}
g5 <- ggplot(data = OJ, mapping = aes(x = PriceCH, y = PriceMM)) +
  geom_point(mapping = aes(shape = Purchase)) +
  geom_smooth()

g5 +  ggtitle("Plot of Citrus Hill Price vs Minute Maid Price \n by Purchase Choice") +
  theme(plot.title = element_text(hjust = 0.5)) +
  xlab("CH Price ($)") + ylab("MM Price ($)")
```

