---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

## Preliminaries

```{r,message=FALSE}
library(tidyverse)
```

## Get our data

```{r}
d <- read.csv("survey-1.csv")
d
```

# Graph 1

### Discussion:

*"Plot of Where Respondent Wants to Live Next After Graduation"*

+ **Top Preference:** New York (5), Dallas (5)
+ **Lowest Preference:** Washington DC (1)
+ **Overall Observation:** Despite the range of cities or regions observed in the graph, the majority of respondents would like to live in a major city after graduation.


```{r, fig.width = 8, fig.height = 8}
# Graph 1
  
ggplot(data = d, 
       mapping = aes(x = reorder(NextCity,NextCity,function(x)-length(x)))) +
  geom_bar() +
  geom_text(
     aes(label=stat(count)),
     stat='count',
     nudge_y=0.125) +
  coord_flip() +
  labs(title = "Next City After Graduation", x = "City", y = "No. of Responses") +
  theme(plot.title = element_text(hjust = 0.5))
```
# Graph 2

### Discussion:

*"Plot of Type of Computer by Major"*

+ **Overall Observation:** Advertising/Communications is the major with the most Mac users, whereas Business has the most Windows PC users. 

  Both         Mac        Windows         Total
---------  ----------   -----------     --------
   2           41            24            67
 2.98%       61.19%        35.83%         100%


```{r, fig.width = 8, fig.height = 8}
# Graph 2
ggplot(data = d, mapping = aes(x = Major)) +
  geom_bar(aes(y = 100 * (..count..)/sum(..count..))) + 
  ylim(0,100) +
  facet_grid(Computer ~ .) +
  geom_text(
     aes(label=stat(count)),
     stat='count',
     nudge_y=0.125) +
  labs(title = "Type of Computer by Major", x = "", y = "Percentage") +
   theme(axis.text.x = element_text(angle = 70, vjust = 1, hjust=1), plot.title = element_text(hjust = 0.5)) 
```
# Graph 3

### Discussion:

*"Plot of Sports Fan by Major"*

> Most Amount of Sports Fans to Least Amount by Major:

1. Advertising, Communications
2. Business
3. Economics, Policy, Government
4. Liberal Arts
5. Engineering/ Science or Math


```{r, fig.width = 8, fig.height = 8}
# Graph 3

ggplot(data = d, aes(x = Major)) +
  geom_bar(mapping = aes(x = Major, fill = Sports), position = "dodge") + 
   geom_text(
     aes(label=stat(count)),
     stat='count',
     nudge_y=0.125) +
  labs(title = "Sports Fan by Major", x = "") +
   theme(axis.text.x = element_text(angle = 70, vjust = 1, hjust=1), plot.title = element_text(hjust = 0.5)) 
```
# Graph 4

### Discussion:

*"Plot of How Much Respondent Likes Math on a Scale of 1-5 by Major"*

+ **Overall Observation:** Science/Math, Liberal Arts, and Engineering majors were the only concentrations not to rate their overall liking of math a 1 or 2. Advertising/Communications varied through the scale, having respondents rate 1 through 5 for their liking of math. 

```{r, fig.width = 8, fig.height = 10}
#Graph 4
ggplot(data = d, mapping = aes(x = LikeMath, y = Major)) +
  geom_jitter(size=5, alpha=0.4) +
  labs(title = "How Much Respondent Likes Math by Major", x = "Rating of 1 (Not Very Much) to 5 (Very Much)", y = "") +
   theme(plot.title = element_text(hjust = 0.5))
```