---
title: "R Notebook"
output: html_notebook
---

```{r}
library(nycflights13)
library(tidyverse)
view(flights)
?flights
```


## Question 1

#### Write a filter expression that returns all flights with an arrival delay of two hours or more

```{r}
arr_delay_2_hrs <- filter(flights, arr_delay >= 120 )
arr_delay_2_hrs
```

## Question 2

#### Write a filter expression that returns all flights that flew to Houston, which has two airports: "IAH" and "HOU".

```{r}
filter(flights, dest == 'IAH' | dest == 'HOU' )
```

## Question 3

#### How many flights have a missing dep_time? Write some code that computes that answer.

+ There are 8,255 flights with missing departure times.

```{r}
nrow(filter(flights, is.na(dep_time)))
```

## Question 4

#### Write an arrange expression that returns all flights sorted be decreasing departure delay. (The first flight should have a/the greatest departure delay.)

```{r}
arrange(flights, desc(dep_delay))
```

## Question 5

#### Write a mutate expression that adds a column mph that gives the speed in miles per hour.

```{r}
flights_mph <- select(flights, 
  year:day,
  distance, 
  air_time
)
mutate(flights_mph,
       hours = air_time / 60,
       mph = distance / hours
)
```